Classifying Human Driving Behavior via Deep Neural Networks

### 2017-06-09 presentation/presentation.tex
updated presentation

%%%%%%%%%%%%%%%%%%%%
%------------------%
%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\begin{frame}
\frametitle{Problem Statement}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.85\textwidth]{project-overall}
%    \caption{General Artificial Neuron}
    \label{fig:diagnosticdriving}
\end{figure}
\begin{itemize}
\item Modern car systems collect real-time data of the car status and driving behavior of the driver
\item Such data is very valuable for healthcare and research
\item {\color{blue} Goal}: use driving behavior data to diagnose medical conditions
\end{itemize}
\end{frame}

@@

\begin{itemize}
\item An artificial neuron has input signals, weights, bias, and activation function \cite{raschka2015python}
\end{itemize}
\end{frame}

@@

$$\vec{h} = \bold{f}(\vec{x}\bold{v}+\vec{c}) = \bold{f}(\vec{X}\bold{V})$$

@@

@@

Error Function:
$$J(\bold{V}, \bold{W}) = \frac{1}{2}\sum_{i}(y_i-o_i)^2 =\frac{1}{2}\sum_{i}(y_i-g(\bold{h}(\vec{X}\bold{V})\bold{W_i}))^2$$

@@

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Neural Networks - Back Propagation}
Update $V_{ij}$ - $i$th neuron for $j$th input:
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.9\textwidth]{../paper/pictures/figures/BP2.png}
    \caption{Back-propagation for $V_{ij}$}
    \label{fig:BP2}
\end{figure}
$$
{{V_{ij}}^{next}}
= V_{ij} - \eta\frac{\partial J}{\partial V_{ij}}
= V_{ij} - \eta\frac{\partial J}{\partial h_i}\frac{\partial h_i}{\partial h'_i}\frac{\partial h'_i}{\partial V_{ij}}
= V_{ij} - \eta\sum_k(\delta_kw_{ki})h_i(1-h_i)X_j
$$

@@

\column{0.5\textwidth}
\begin{itemize}
\item Recurrent Neural Network
\item Four gates and Memory Cells handle long term dependencies
\end{itemize}
\end{columns}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Long Short Term Memory Networks (LSTM)}
Input gate:
$$\vec{i^t} = \bold{sigm}(\vec{X^t}\bold{T_{n,m}^{ii}} + \vec{H^{t-1}}\bold{T_{m,m}^{oi}})$$

@@

Result:
	$$\vec{h^t} = \vec{c^t} * \vec{o^t}$$
\end{frame}

@@

Auto-encoder is a neural network to attempt to copy its inputs to its outputs
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Auto-encoder (AE) - Multiple layer AE}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.6\textwidth]{../paper/pictures/figures/example_MAE.png}
    \caption{Multilayer Auto-encoder Example}
    \label{fig:example_MAE}
\end{figure}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%
%------------------%
%%%%%%%%%%%%%%%%%%%%
\section{Data Set}
%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\begin{figure}[t!]
    \centering
    \includegraphics[width=\textwidth]{figure-simulator-cropped}
    \caption{Driving Simulator at CHOP}
    \label{fig:simulator}
\end{figure}
\end{frame}

>>>>

%%%%%%%%%%%%%%%%%%%%
%------------------%
%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\begin{frame}
\frametitle{Problem Statement}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.85\textwidth]{./pictures/figures/project-overall.pdf}
%    \caption{General Artificial Neuron}
    \label{fig:diagnosticdriving}
\end{figure}
\begin{itemize}
\item Modern car systems collect real-time data of the car status and driving behavior of the driver
\item Such data is very valuable for healthcare and research
\item {\color{blue} Goal}: use driving behavior data to diagnose medical conditions
\end{itemize}
\end{frame}

@@

\begin{itemize}
\item The concept of artificial neurons or perseptrons was introduced by Warren McCullock and Walter Pitts \cite{raschka2015python}
\item An artificial neuron has input signals, weights, bias, and activation function
\end{itemize}
\end{frame}

@@

Pass inputs $\vec{x}$ to outputs through hidden layers \cite{murphy2012machine}
$$\vec{h} = \bold{f}(\vec{x}\bold{v}+\vec{c}) = \bold{f}(\vec{X}\bold{V})$$

@@

\begin{itemize}
\item Passes an error from the output layer to hidden layers \cite{murphy2012machine}
\item Assumption:

@@

Error Function:
$$J(\bold{V}, \bold{W}) = \frac{1}{2}\sum_{i}(y_i-o_i)^2 =\frac{1}{2}\sum_{i}(y_i-g(\bold{h}(\vec{X}\bold{V})\bold{W_i}))^2$$
\end{itemize}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Neural Networks - Back Propagation}
Update $V_{ij}$ - $i$th neuron for $j$th input:
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.9\textwidth]{../paper/pictures/figures/BP2.png}
    \caption{Back-propagation for $V_{ij}$}
    \label{fig:BP2}
\end{figure}
$$
{{V_{ij}}^{next}}
= V_{ij} - \eta\frac{\partial J}{\partial V_{ij}}
= V_{ij} - \eta\frac{\partial J}{\partial h_i}\frac{\partial h_i}{\partial h'_i}\frac{\partial h'_i}{\partial V_{ij}}
= V_{ij} - \eta\sum_k(\delta_kw_{ki})h_i(1-h_i)X_j
$$
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Neural Networks - Back Propagation}
Update $V_{ij}$ - $i$th neuron for $j$th input:
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.9\textwidth]{./pictures/figures/BP2_with_error.png}
    \caption{Back-propagation for $V_{ij}$}
    \label{fig:BP2}
\end{figure}
$$
{{V_{ij}}^{next}}
= V_{ij} - \eta\frac{\partial J}{\partial V_{ij}}
= V_{ij} - \eta\frac{\partial J}{\partial h_i}\frac{\partial h_i}{\partial h'_i}\frac{\partial h'_i}{\partial V_{ij}}
= V_{ij} - \eta\sum_k(\delta_kw_{ki})h_i(1-h_i)X_j
$$
\end{frame}

@@

\column{0.5\textwidth}
\begin{itemize}
\item LSTM is a type of RNN introduced by Hochreiter and Schmidhuber \cite{hochreiter1997long}
\item Four gates and Memory Cells handle long term dependencies
\end{itemize}
\end{columns}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Long Short Term Memory Networks (LSTM)}
\begin{columns}
\column{0.5\textwidth}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.8\textwidth]{./pictures/figures/LSTM_input.png}
    \caption{LSTM Input}
    \label{fig:LSTM_input}
\end{figure}

\column{0.5\textwidth}
\begin{itemize}
\item Blue = Current Input
\item Green = Previous Output
\end{itemize}
\end{columns}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Long Short Term Memory Networks (LSTM)}
\begin{columns}
\column{0.5\textwidth}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.8\textwidth]{./pictures/figures/LSTM_input_gate.png}
    \caption{LSTM Input Gate}
    \label{fig:LSTM_input_gate}
\end{figure}

\column{0.5\textwidth}
Input gate:
$$\vec{i^t} = \bold{sigm}(\vec{X^t}\bold{T_{n,m}^{ii}} + \vec{H^{t-1}}\bold{T_{m,m}^{oi}})$$
\end{columns}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Long Short Term Memory Networks (LSTM)}
\begin{columns}
\column{0.5\textwidth}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.8\textwidth]{./pictures/figures/LSTM_input_module_gate.png}
    \caption{LSTM Input Module Gate}
    \label{fig:LSTM_input_gate}
\end{figure}

\column{0.5\textwidth}
Input modulation gate:
$$\vec{m^t} = \bold{tanh}(\vec{X^t}\bold{T_{n,m}^{im}} + \vec{H^{t-1}}\bold{T_{m,m}^{om}})$$
\end{columns}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Long Short Term Memory Networks (LSTM)}
\begin{columns}
\column{0.5\textwidth}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.8\textwidth]{./pictures/figures/LSTM_forget_gate.png}
    \caption{LSTM Forget Gate}
    \label{fig:LSTM_forget_gate}
\end{figure}

\column{0.5\textwidth}
Forget gate:
$$\vec{f^t} = \bold{sigm}(\vec{X^t}\bold{T_{n,m}^{if}} + \vec{H^{t-1}}\bold{T_{m,m}^{of}})$$
\end{columns}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Long Short Term Memory Networks (LSTM)}
\begin{columns}
\column{0.5\textwidth}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.8\textwidth]{./pictures/figures/LSTM_output_gate.png}
    \caption{LSTM Output Gate}
    \label{fig:LSTM_output_gate}
\end{figure}

\column{0.5\textwidth}
Output gate:
$$\vec{o^t} = \bold{sigm}(\vec{X^t}\bold{T_{n,m}^{io}} + \vec{H^{t-1}}\bold{T_{m,m}^{oo}})$$
\end{columns}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Long Short Term Memory Networks (LSTM)}
\begin{columns}
\column{0.5\textwidth}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.8\textwidth]{./pictures/figures/LSTM_memory_cells.png}
    \caption{LSTM Memory Cells}
    \label{fig:LSTM_memory_cells}
\end{figure}

\column{0.5\textwidth}
Memory cells:
$$\vec{c^t} = \vec{i^t} * \vec{m^t} + \vec{f^t} * \vec{c^{t-1}}$$
\end{columns}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Long Short Term Memory Networks (LSTM)}
\begin{columns}
\column{0.5\textwidth}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.8\textwidth]{./pictures/figures/LSTM_output.png}
    \caption{LSTM Output}
    \label{fig:LSTM_output}
\end{figure}

\column{0.5\textwidth}
Output:
$$\vec{h^t} = \vec{c^t} * \vec{o^t}$$
\end{columns}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Long Short Term Memory Networks (LSTM)}
Math model \cite{zaremba2014recurrent}

Input gate:
$$\vec{i^t} = \bold{sigm}(\vec{X^t}\bold{T_{n,m}^{ii}} + \vec{H^{t-1}}\bold{T_{m,m}^{oi}})$$

@@

Output:
$$\vec{h^t} = \vec{c^t} * \vec{o^t}$$
\end{frame}

@@

Auto-encoder is a neural network to attempt to copy its inputs to its outputs \cite{Goodfellow-et-al-2016}
\end{frame}

@@

\begin{itemize}
\item Multiple encoders and decoders
\item Pretraining process \cite{hinton2006reducing}
\end{itemize}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%
%------------------%
%%%%%%%%%%%%%%%%%%%%
\section{Data Set}
%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\begin{figure}[t!]
    \centering
    \includegraphics[width=\textwidth]{./pictures/figures/figure-simulator-cropped.pdf}
    \caption{Driving Simulator at CHOP}
    \label{fig:simulator}
\end{figure}
\end{frame}
